### 2017-11-02 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
Update hypothesis test

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}

@@

The \textbf{boundary values} of the critical region are called the critical values.
\section{Method}
\begin{enumerate}
\item Establish the null and alternative hypothesis ($H_0$ and $H_1$)
\item Define distribution under $H_0$
\item Decide on the significance level
\item Collect data, state the test statistic, X=
\item Calculate the probability of obtaining the test statistic or a more extreme result (same direction as $H_1$)
\item Compare this to the sig level as a decimal
\begin{itemize}
\item If \textbf{greater} than the sig level, it is a \textbf{non significant} result, it is not in the critical region and we \textbf{do not} reject $H_0$
\item If \textbf{less} than sig level, it is a \textbf{significant result}, it is in the critical region and we \textbf{reject} $H_0$ 
\end{itemize}
\item Interpret the results in terms of the original claim
\end{enumerate}

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

@@

The \textbf{boundary values} of the critical region are called the critical values.
\section{Method}
\begin{enumerate}
\item Establish the null and alternative hypothesis ($H_0$ and $H_1$)
\item Define distribution under $H_0$
\item Decide on the significance level
\item Collect data, state the test statistic, X=
\item Calculate the probability of obtaining the test statistic or a more extreme result (same direction as $H_1$)
\item Compare this to the sig level as a decimal
\begin{itemize}
\item If \textbf{greater} than the sig level, it is a \textbf{non significant} result, it is not in the critical region and we \textbf{do not} reject $H_0$
\item If \textbf{less} than sig level, it is a \textbf{significant result}, it is in the critical region and we \textbf{reject} $H_0$ 
\end{itemize}
\item Interpret the results in terms of the original claim
\end{enumerate}
\subsection{Example}
\textbf{Establish the null and alternative hypothesis}\\
$H_0:p=0.5$\\
$H_1:p>0.5$\\
\\
\textbf{Define the distribution under $\mathbf{H_O}$}\\
Under $H_0$ $X\sim B(15,0.5)$\\
\\
\textbf{Decide on the significance level}\\
$5\%$\\
\\
\textbf{Collect data, state the test statistic}\\
X=12\\
\\
\textbf{Calculate the probability of obtaining the test statistic or a more extreme result}\\
\begin{tabular}{r l}
$P(X\geqslant 12)$&$=1-P(X\leqslant 11)$\\
&$=1-0.9824$\\
&$=0.0176$\\
\end{tabular}
\\
\textbf{Compare this to the sig level as a decimal}
$0.0176<0.05$\\
\\
\textbf{Interpret the results in terms of the original claim}\\
There is evidence to reject $H_0$ in favour of $H_1$. The test is significant.
\subsection{Finding critical values}
We require a value c such that:\\
$P(X\geqslant c)<0.05$\\
$1-P(X\leqslant c-1)<0.05$\\
$P(X\leqslant c-1)>0.95$\\
\\
\textbf{Test against tables}\\
$P(X<11)=0.9824$\\
\\
$c-1=11$\\
$c=12$
\subsection{Two tailed tests}
